Text embedding models yield high-resolution insights into conceptual knowledge from short multiple-choice quizzes

### 2023-10-25 paper/main.tex

After watching \textit{Four Fundamental Forces}, predicted knowledge for
held-out questions that were answered correctly (from the second quiz;
Fig.~\ref{fig:predictions}, middle column) exhibited a significantly shift relative
to held-out questions that were answered incorrectly. This held when we included all
questions in the analysis ($\U = 58332,~p < 0.001$), when we predicted knowledge
across-lectures (\textit{Four Fundamental Forces}: $\U = 6749.5,~p = 0.014$;
\textit{Birth of Stars}: $\U = 8480,~p = 0.016$), and when we predicted
knowledge at the embedding coordinates of held-out \textit{Four Fundamental
Forces} questions using other \textit{Four Fundamental Forces} questions from
the same quiz and participant ($\U = 7224,~p < 0.001$). This difference did
\textit{not} hold for within-lecture knowledge predictions at 
knowledge at embedding space coordinates of \textit{Birth of Stars} questions ($\U = 7419,~p = 0.739$). Again, we suggest that this might reflect a
floor effect whereby knowledge about the content of the \textit{Birth of Stars}
material is relatively low everywhere in that region of text embedding space.

>>>>

After watching \textit{Four Fundamental Forces}, predicted knowledge for
held-out questions that were answered correctly (from the second quiz;
Fig.~\ref{fig:predictions}, middle column) exhibited a significant positive
shift relative to held-out questions that were answered incorrectly. This held
when we included all questions in the analysis ($\U = 58332,~p < 0.001$), when
we predicted knowledge across-lectures (\textit{Four Fundamental Forces}: $\U =
6749.5,~p = 0.014$; \textit{Birth of Stars}: $\U = 8480,~p = 0.016$), and when
we predicted knowledge at the embedding coordinates of held-out \textit{Four
Fundamental Forces} questions using other \textit{Four Fundamental Forces}
questions from the same quiz and participant ($\U = 7224,~p < 0.001$). This
difference did \textit{not} hold for within-lecture knowledge predictions at
knowledge at embedding space coordinates of \textit{Birth of Stars} questions
($\U = 7419,~p = 0.739$). Again, we suggest that this might reflect a floor
effect whereby, at that point in the participants' training, their knowledge
about the content of the \textit{Birth of Stars} material is relatively low
everywhere in that region of text embedding space.
